### 2021-04-04 Chapter-4/Chapter-4.tex
Updates from Overleaf

\subsubsection{Math Notations}
We assume a program ($\beta$) has $K$ as its sensitive input. $K$ should be 
a finite set of keys. The program also takes known messages $M$ as its input. 
During an AES encryption, for example, 
$\beta$ is the encryption function. $K$ is the set of all possible AES keys, 
and $M$ represents the set consisting of all plaintext messages to be encrypted. In a real execution, an adversary may have 
some observations ($O$) of the program. This paper only
uses secret-dependent control flows and secret-dependent data 
accesses as observations.

@@

In
contrast, an \emph{average} estimate based on random secret input information is around
1 bit, as shown in \S\ref{sec:background_leak} and Table~\ref{shtable}, is
not very useful in practice as an attacker is able to get much more leaked
information in some attack scenarios.

@@

\section{Evaluation}

>>>>

We assume a program ($\beta$) has $K$ as its sensitive input. $K$ should be 
a finite set of keys. The program also takes known messages $M$ as its input. 
During an AES encryption, for example, 
$\beta$ is the encryption function. $K$ is the set of all possible AES keys, 
and $M$ represents the set consisting of all plaintext messages to be encrypted. In a real execution, an adversary may have 
some observations ($O$) of the program. This paper only
uses secret-dependent control flows and secret-dependent data 
accesses as observations.

@@

In
contrast, an \emph{average} estimate based on random secret input information is around
1 bit, as shown in the previous section and Table~\ref{shtable}, is
not very useful in practice as an attacker is able to get much more leaked
information in some attack scenarios.

@@

\section{Evaluation}
\begin{table}[]
    \centering\small\footnotesize
    \caption{Evaluation results overview: Name, Side-channel Leaks\,(Leaks), 
        Secret-dependent Control-flows\,(CF), Secret-dependent Data-flows\,(DF),
        The number of instructions\,(\# Instructions), Symbolic Execution\,(SE) and Monte Carlo\,(MC) time.
    }\label{table:over_result}

%    \resizebox{1.9\columnwidth}{!}{
    \begin{threeparttable}
    \begin{tabular}{l@{}r@{~~}rrr@{~~}rr}
        \hline
        \textbf{Name}   & \textbf{\# Leaks} & \textbf{\# CF}         & \textbf{\# DF}
                           & \textbf{\# Instructions}    & \textbf{SE} & \textbf{MC}                                                    \\\hline
                                                 &                        &                     &                      &              & ms        & ms              \\\cline{6-7}
        AES\tnote{1}               & 68                     & 0                   & 68                   & 39,855        & 512     & 1,052         \\
        AES\tnote{2}                & 68                     & 0                   & 68                   & 39,855       & 520    & 1,057         \\
        AES\tnote{4}                & 75                     & 0                   & 75                   & 1,704        & 231    & 9,199        \\
        AES\tnote{5}                & 88                     & 0                   & 88                   & 1,350        & 36      & 1,924         \\
        AES\tnote{6}                & 88                     & 0                   & 88                   & 1,350        & 35      & 1,961        \\
        AES\tnote{7}                & 88                     & 0                   & 88                   & 1,420        & 36     & 2,161        \\
        AES\tnote{8}                & 88                     & 0                   & 88                   & 1,586        & 43      & 1,631        \\
        DES\tnote{1}                & 15                     & 0                   & 15                   & 4,596        & 58      & 162          \\
        DES\tnote{2}                & 15                     & 0                   & 15                   & 4,596        & 57      & 162           \\
        DES\tnote{4}                & 6                      & 0                   & 6                    & 2,976         & 163    & 4,677         \\
        DES\tnote{5}                & 8                      & 0                   & 8                    & 2,593         & 166    & 6,509        \\
        DES\tnote{6}                & 8                      & 0                   & 8                    & 2,593        & 165    & 5,975        \\
        DES\tnote{7}                & 8                      & 0                   & 8                    & 4,260         & 182    & 5,292        \\
        DES\tnote{8}                & 6                      & 0                   & 6                    & 8,272         & 229     & 5,152      \\
                           &                        &                     &                      &                  & seconds   & seconds               \\\cline{6-7}
        Chacha20\tnote{3}           & 0                      & 0                   & 0                    & 149,353        & 2     & 0             \\  
        Poly1305\tnote{3}           & 0                      & 0                   & 0                    & 1,213,937      & 15    & 0             \\
        Argon2i\tnote{3}            & 0                      & 0                   & 0                    & 4,595,142       & 37    & 0             \\
        Ed25519\tnote{3}            & 0                      & 0                   & 0                    & 5,713,619       & 271   & 0            \\
        ECDSA\tnote{1}              & 6                      &    6                & 0                    &  4,214,946     &  48   &   31       \\ 
        ECDSA\tnote{2}              &   4                   &   4                 & 0                    &  4,192,558    & 102   & 1639          \\   
        ECDSA\tnote{5}              &  5                    & 4                   & 1                    &  8,248,322       & 101     & 62           \\   
        ECDSA\tnote{6}              &  5                    & 4                   & 1                    &  8,263,599      & 100     & 58            \\   
        ECDSA\tnote{7}              &  5                    & 4                   & 1                    &  6,100,465       & 76      & 42                  \\  
        ECDSA\tnote{8}              & 0                      &  0                   &    0               &  10,244,076       &  121     & 0                  \\  
        ECDSA\tnote{9}              & 0                      &  0                   &  0                 &  9,266,191          & 102     & 59        \\

                           &                        &                     &                      &                 & minutes   & minutes         \\\cline{6-7}
        RSA\tnote{1}                & 6                       & 6                   & 0                    & 22,109,246    & 39     & 41           \\
        RSA\tnote{2}                & 12                      & 12                  & 0                    & 24,484,441    & 44     & 251           \\
        RSA\tnote{4}                & 107                    & 105                 & 2                    & 17,002,523   & 23      & 428           \\
        RSA\tnote{5}                & 38                     & 27                  & 11                   & 14,468,307   & 29     & 436          \\
        RSA\tnote{6}                & 36                     & 27                  & 9                    & 15,285,210   & 40     & 714          \\
        RSA\tnote{7}                & 31                     & 22                  & 9                    & 16,390,750   & 34      & 490         \\
        RSA\tnote{8}                & 4                      &  4                  & 0                    & 18,207,016   & 8      & 53          \\
        RSA\tnote{9}                & 8                      &  8                  & 0                    & 18,536,796    & 5      & 780         \\
        RSA\tnote{10} & 11& 9& 2& 9,527,231& 2 &38\\
        RSA\tnote{11} & 14& 14& 0& 10,513,606& 14 &503 \\
        RSA\tnote{12}               & 8                      &  8                  & 0                    & 27,407,986    & 113    & 6560       \\

        Total              & 904                    & 241                 & 663                & 167,141,947      & 341m  & 10,232m     \\\hline
    \end{tabular}
\end{threeparttable}
\begin{tablenotes}
    \scriptsize

    \item[1] mbedTLS\,2.5  ~~~~\item[2] mbedTLS\,2.15 ~\item[3] Monocypher\,3.0 \\
    \item[4] OpenSSL\,0.9.7  ~~\item[5] OpenSSL\,1.0.2f  \item[6] OpenSSL\,1.0.2k \\
    \item[7] OpenSSL\,1.1.0f ~\item[8] OpenSSL\,1.1.1 ~\item[9] OpenSSL\,1.1.1g \\
    \item[10] Libgcrypt\,1.6.1 \item[11] Libgcrypt\,1.7.3 \item[12] Libgcrypt\,1.8.5\\
\end{tablenotes}
\vspace*{-20pt}

\end{table}

\subsection{Case Studies}

\subsubsection{Symmetric Ciphers: DES and AES}\label{eval:sym}
We test both DES and AES ciphers from mbedTLS and OpenSSL\@. Both cipher
implementations apply lookup tables, which improve performance but can also introduce side-channels as well. During our evaluation, we find mbedTLS 2.5 and 2.15.1 have the same implementation of AES and DES\@. Therefore, our tool reports the same leakages for both versions.

We find that the DES implementations in both mbedTLS and OpenSSL have several
severe information leakages in the key schedule function.
We do not see any mitigation
in the new version. We think it is not seen as worth the engineering
efforts given the life cycles of DES\@.

\tool{} shows that the AES in OpenSSL 1.1.1 has less leakage than other versions. 
OpenSSL 1.1.1 uses 1KB lookup tables with 8-bit entries, unlike older versions that use a table with 32-bit entries. Our tool suggests a smaller lookup table might mitigate side-channel vulnerabilities.

\subsubsection{Monocypher}\label{eval:mono}
Monocypher is a small, easy to use cryptographic library with
performance comparable to LibSodium~\cite{libsodium} and NaCl~\cite{bernstein2012security}. 
We choose four ciphers that are 
designed to be side-channel resistant from the library.
Because those ciphers have no 
data flow from secrets to branch conditions and load addresses.
Monocypher should be safe under our threat models. 
We analyze those ciphers with \tool{}, and it reports no leaks.
This indicates that \tool{} is effective for validating countermeasures.
